---
title: ""
author: ""
date: ""
output: 
  pdf_document:
     keep_tex: yes
     includes:
      in_header: header.tex
---
<!-- ************************************************************************************************--> 
<!-- **********************************BEGIN APPENDICES**********************************************--> 
<!-- ************************************************************************************************--> 
\FloatBarrier
\newpage



<!-- ************************************DATA FITS************************************************--> 
#Appendix A. Detailed Fit to Length Composition Data{#append_a} 


```{r, results='asis'}
plot.vec = grep("comp_lenfit_flt", LenComp_mod1$basename)
#plot.vec = c(1:4, 8, 12:15, 19, 23:25, 29, 33:36, 40, 44, 48, 52)

for (a in 1:length(plot.vec)){

  cat('\n![', LenComp_mod1[plot.vec[a],caption_col], ' \\label{fig:length_fits}](r4ss/plots_mod1/', LenComp_mod1[plot.vec[a], path_col], ')\n', sep='')
  
}

```

\FloatBarrier

#Appendix B. Detailed Fit to Age Composition Data{#append_b} 

```{r, results='asis'}
plot.vec = grep("comp_agefit_flt", AgeComp_mod1$basename)
#plot.vec = c(1:5, 9:13, 17:19, 23:25)


for (a in 1:length(plot.vec)){

  cat('\n![', AgeComp_mod1[plot.vec[a],caption_col], ' \\label{fig:age_fits}](r4ss/plots_mod1/', AgeComp_mod1[plot.vec[a], path_col], ')\n', sep='')
  
}

```


\FloatBarrier


\newpage


<!-- ************************************AUXILARY FILES************************************************ --> 
#Appendix C. List of Auxiliary Files Available

The listed files are also available as auxiliary files to accompany the assessment document:

\begin{enumerate}
  \item Numbers at age for female and male `r spp` (Petrale natagef.csv and Petrale natagem.csv)
  \item The `r spp` Stock Synthesis 3.30.13 model files
  
  \begin{enumerate}
    \item 2019petrale.dat
    \item 2019petrale.ctl
    \item forecast.ss
    \item starter.ss
  \end{enumerate}
\end{enumerate}

\newpage